A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Add callsite description

From the figure, we observe that majority of inputs to Core \eval functions are
expressions in contrast to package \eval calls which receive mostly environments
as inputs. In fact, \PackageEnvironmentInputEvalCallPerc of \eval calls in
packages receive environments as input expressions.

Now, we turn our attention to the expressions passed as input to \eval.

@@

\subsection{Provenance}

Here we talk about where the input of an eval comes from.

>>>>

From the figure, we observe that majority of inputs to Core \eval functions are
expressions in contrast to package \eval calls which receive mostly environments
as inputs. In fact, \PackageEnvironmentInputEvalCallPerc of \eval calls in
packages receive environments as input expressions. There are only four
callsites in package evals that receive environments as expressions.
\begin{itemize}
\item \c{ggplot2::ggproto} contributes to 99.9\% of package \eval calls that
receive environments as input.
\item \c{R6::generator_funs} function contributes to only 936 \eval calls and
implements the same functionality as \c{ggplot2::ggproto} but for the \emph{R6}
OOP system.
\item \c{future::backtrace} function applies \eval to a future object which is
implemented as an environment. This is called only once.
\item \c{RModel::str.RMmodel} function overloads the core \c{str} method for its
\c{RModel} objects and maps \eval exactly like \c{str}. This is called only
once.
\end{itemize}

\subsubsection{Provenance}

In this section we turn our attention to the \AllExpressionInputEvalCallPerc
expressions passed as input to \eval. There are multiple ways to obtain
expressions in R.

@@
